Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-10 paper.tex
Some AIML cites.

\footnote{Wilcox identifies several shortcomings with the expressive
  power of AIML, proposing ChatScript as a
  replacement~\cite{wilcox:2010}.  At present AIML's community and
  diversity of third-party implementations make it preferable.}

  We leverage
the AIML language developed for AliceBot~\cite{alicebotxxx}, which has
won several Turing contests. \textbf{XXX more precise here XXX}

>>>>

We leverage AIML~\cite{aiml:2005},%
\footnote{Wilcox identifies several shortcomings with the expressive
  power of AIML, proposing ChatScript as a
  replacement~\cite{wilcox:2010}.  At present AIML's community and
  diversity of third-party implementations make it preferable.}
the markup language developed for AliceBot, three-time winner of the
Loebner Prize, a restricted Turing Test competition for chat bots.
